---
title: "Donald's Favorables - Fake News, Sad"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(readr)
library(flexdashboard)
library(forecast)
library(xtable)
library(lubridate)
library(pollstR)

# Pull and process data
rolling_window = 14 #Set to be a changable option

today <- ymd(format(Sys.time(), '%Y-%m-%d'))
start <- today %m-% months(11:11) # Set this to a changeable variable

poll_name <- "donald-trump-favorable-rating"
polls <- pollster_charts_polls(poll_name)[["content"]]

favorable_data <- aggregate(Favorable ~ end_date, polls, mean)
favorable_data <- favorable_data[order(as.Date(favorable_data$end_date, format="%Y-%m-%d")),]
favorable_data <- subset(favorable_data, favorable_data$end_date >= start)

donald_roll <- rollmean(favorable_data$Favorable, rolling_window)

donald_cast <- forecast(donald_roll)
forecastframe <- data.frame(donald_cast)
```

# Introduction {.sidebar}
###Dashboard Data
* Distribution
* Forecast Plot
* Rolling Average of Polls
* Smoother: 14

###Date Range
```{r}
h4(paste(start," to ",today, sep=""))

```

###Histogram Bins:
```{r}
selectInput("n_breaks", label = "Number of Bins:", choices = c(10, 20, 50), selected = 20)
```

# Donald's Favorables

Column {.tabset}
-------------------------------------
### Favorable Histogram
```{r echo = FALSE, comment=NA}
renderPlot({
  hist(favorable_data$Favorable
    , main = paste("Polling Distribution Since: ", start,sep="")
    , xlab = "Favorability Percent"
    , ylab = "Count of Observations"
    , breaks = as.numeric(input$n_breaks)
    , col = "dodgerblue2")
  }
)
```

### Forecast Chart
``````{r echo = FALSE, comment=NA}
renderPlot({
  plot(donald_cast, main = "Plot of Forecast"
       , xlab = "Polling Count"
       , ylab = "Favorability Percent")
  }
)
```

### Supporting Data
```{r echo = FALSE, comment=NA}
h3(paste("Polling Performance Since: ", start, sep = ""))

h5(paste("    - The median for the time period is: "
      , format(round(median(na.omit(favorable_data$Favorable)), 2), nsmall = 2), sep=""))

h5(paste("    - The mean of percent final score is: "
      , format(round(mean(na.omit(favorable_data$Favorable)), 2), nsmall = 2), sep=""))

h3("Forecast of Donald's Approval")
h5("80/95 Upper and Lower Prediciton Interval s")
renderTable({
  forecastframe
})
```

Source data available via:
http://elections.huffingtonpost.com/pollster/api
